Reasonably Programmable Literal Notation

### 2018-06-19 icfp18/syntax-icfp18.tex
moved note about first class modules to 2.1.2

@@

\begin{figure}
\vspace{-5px}
\begin{displaymath}
\begin{array}{l}
  \text{\li{$regex `(GC$(DNA.any_base)GC)`}}\\[-10px]
  \xymatrix{
  ~ \ar[d]^{\text{The applied TLM lexes and parses the literal body to generate the \textbf{proto-expansion}.}} \\ ~
  % \text{\li{Regex.Seq(Regex.Str "GC", Regex.Seq(spliced<4..15 : Regex.t>, Regex.Str "GC"))}} \ar[d]^f\\ 
  }\\[-5px]
  \text{\li{Regex.Seq(Regex.Str "GC", Regex.Seq(spliced<4..15 : Regex.t>, Regex.Str "GC"))}}\\[-10px]
  \xymatrix{
  ~ \ar[d]^{\text{The system performs proto-expansion validation and generates the \textbf{final expansion}.}} \\ ~
  % \text{\li{Regex.Seq(Regex.Str "GC", Regex.Seq(spliced<4..15 : Regex.t>, Regex.Str "GC"))}} \ar[d]^f\\ 
  }\\[-5px]
  \text{\li{Regex.Seq(Regex.Str "GC", Regex.Seq(DNA.any_base, Regex.Str "GC"))}}
\end{array}
\end{displaymath}
\caption{Expansion of TLM applications occurs in two steps.}
\vspace{-5px}
\label{fig:expansion}
\end{figure}

@@

\subsubsection{Other Implementation Strategies}
Although \li{ocamllex} and Menhir are powerful tools, they are not right for every parsing job. For example, we might want to use a different parser generator, a parser combinator library \cite{Hutton1992d}, or post-process the result of calling an existing parser to produce a corresponding proto-expansion. Fortunately, it is easy to bypass \li{ocamllex} and Menhir: 
%The most obvious method is to define a trivial lexer that reads the entire literal body into a single token, and a trivial parser with one semantic action. In fact, this is not actually necessary because the system does not interface with \li{ocamllex} and Menhir directly. Rather, it is the job of the user's build system to make sure that by the time the compiler is invoked, these tools have already been invoked as necessary to produce ordinary OCaml modules satisfying the expected interface. It is just as well to implement this interface manually. 
the \li{Relit} library includes a trivial lexer, \li{Relit.TrivLexer}, and a few functors that take care of the necessary boilerplate in situations where we simply want to define the parser as a function of type \li{string => Relit.ProtoExpr.t}. For example, the supplement briefly describes how \li{$re_expr} can be expressed in terms of the Reason parser, a parse tree serializer and a tree transformation. It also details how the \li{$html} TLM shown previously is implemented using an existing, ``production grade'' HTML parsing library, \li{Markup.ml} \cite{markupml}, together with a simple post-processing step. It is also worth noting that although there is no mechanism for applying TLMs at the module level, this can be emulated by using OCaml's first class modules.

>>>>

It is also worth noting here that although there is no direct mechanism for applying TLMs at the module level, this can be achieved by using OCaml's first class modules \cite{ocaml-manual}.

@@

\begin{figure}
\vspace{-10px}
\begin{displaymath}
\begin{array}{l}
  \text{\li{$regex `(GC$(DNA.any_base)GC)`}}\\[-10px]
  \xymatrix{
  ~ \ar[d]^{\text{The applied TLM lexes and parses the literal body to generate the \textbf{proto-expansion}.}} \\ ~
  % \text{\li{Regex.Seq(Regex.Str "GC", Regex.Seq(spliced<4..15 : Regex.t>, Regex.Str "GC"))}} \ar[d]^f\\ 
  }\\[-5px]
  \text{\li{Regex.Seq(Regex.Str "GC", Regex.Seq(spliced<4..15 : Regex.t>, Regex.Str "GC"))}}\\[-10px]
  \xymatrix{
  ~ \ar[d]^{\text{The system performs proto-expansion validation and generates the \textbf{final expansion}.}} \\ ~
  % \text{\li{Regex.Seq(Regex.Str "GC", Regex.Seq(spliced<4..15 : Regex.t>, Regex.Str "GC"))}} \ar[d]^f\\ 
  }\\[-5px]
  \text{\li{Regex.Seq(Regex.Str "GC", Regex.Seq(DNA.any_base, Regex.Str "GC"))}}
\end{array}
\end{displaymath}
\vspace{-4px}
\caption{Expansion of TLM applications occurs in two steps.}
\vspace{-6px}
\label{fig:expansion}
\end{figure}

@@

\subsubsection{Other Implementation Strategies}
Although \li{ocamllex} and Menhir are powerful tools, they are not right for every parsing job. For example, we might want to use a different parser generator, a parser combinator library \cite{Hutton1992d}, or post-process the result of calling an existing parser to produce a corresponding proto-expansion. Fortunately, it is easy to bypass \li{ocamllex} and Menhir: 
%The most obvious method is to define a trivial lexer that reads the entire literal body into a single token, and a trivial parser with one semantic action. In fact, this is not actually necessary because the system does not interface with \li{ocamllex} and Menhir directly. Rather, it is the job of the user's build system to make sure that by the time the compiler is invoked, these tools have already been invoked as necessary to produce ordinary OCaml modules satisfying the expected interface. It is just as well to implement this interface manually. 
the \li{Relit} library includes a trivial lexer, \li{Relit.TrivLexer}, and a few functors that take care of the necessary boilerplate in situations where we simply want to define the parser as a function of type \li{string => Relit.ProtoExpr.t}. For example, the supplement briefly describes how \li{$re_expr} can be expressed in terms of the Reason parser, a parse tree serializer and a tree transformation. It also details how the \li{$html} TLM shown previously is implemented using an existing, ``production grade'' HTML parsing library, \li{Markup.ml} \cite{markupml}, together with a simple post-processing step.
